---
output: github_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%")
```

# tiltIndicatorAfter

The goal of tiltIndicatorAfter is to conduct post-processing of four indicators created from the tiltIndicator package. The post-processing process cleans the data, adds additional columns, and creates subsets for Netherlands and 20 sample companies. The processed output from the tiltIndicatorAfter package is the final output for the user.

This repository hosts only public code and may only show only fake data.

## Installation

You can install the development version of tiltIndicator from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("2DegreesInvesting/tiltIndicatorAfter")
```

## Example

```{r}
library(tiltIndicatorAfter)

packageVersion("tiltIndicatorAfter")

companies

matches_mapper

ecoinvent_activities

ecoinvent_inputs

# PCTR

pctr_product

pctr_product_final <- pctr_product |>
  prepare_pctr_product(companies, ecoinvent_activities, matches_mapper)
pctr_product_final

pctr_company

pctr_company_final <- pctr_company |> 
  prepare_pctr_company(pctr_product, companies, ecoinvent_activities, matches_mapper)
pctr_company_final
```
