---
title: "tiltIndicatorAfter_runner"
author: "Kalash"
date: "2023-07-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The tiltIndicatorAfter_runner script uses the output from the tiltIndicatorBefore package as the inputs to the tiltIndicator and tiltIndicatorAfter packages. This script uses the CSV files from the tiltIndicatorBefore package to create the final output of the four indicators. 
To reduce the processing time of tiltIndicator and tiltIndicatorAfter code, this script also uses multiple R sessions to run the job in parallel. The `multisession` technique will produce the final outputs in chunks which all will be combined together after the completion of the job run. 

## Setup
```{r}
library(dplyr, warn.conflicts = FALSE)
library(readr, warn.conflicts = FALSE)
library(tidyr, warn.conflicts = FALSE)
library(purrr, warn.conflicts = FALSE)
library(rappdirs)
library(future)
library(furrr)
library(fs)
library(tiltIndicator)
## devtools::install_github("2DegreesInvesting/tiltIndicatorAfter")
library(tiltIndicatorAfter)
```

## Helper functions to apply multisession and chunks approach

```{r}
options(readr.show_col_types = FALSE)
# Enable computing over multiple workers in parallel
plan(multisession)

# Helpers ----

cache_path <- function(..., parent = cache_dir()) {
  path(parent, ...)
}

cache_dir <- function() {
  user_cache_dir(appname = "tiltIndicatorAfter")
}

nest_chunk <- function(data, .by, chunks) {
  data |>
    nest(.by = all_of(.by)) |>
    mutate(data, chunk = as.integer(cut(row_number(), chunks))) |>
    unnest(data) |>
    nest(.by = chunk)
}

add_file <- function(data, parent_product, parent_company, ext = ".rds") {
  dir_create(parent_product)
  dir_create(parent_company)
  mutate(data, file_product = path(parent_product, paste0(chunk, ext)), file_company = path(parent_company, paste0(chunk, ext)))
}

pick_undone <- function(data) {
  data |>
    add_done() |>
    filter(!done_product | !done_company)
}

add_done <- function(data, file_product, file_company) {
  mutate(data, done_product = file_exists(file_product), done_company = file_exists(file_company))
}

```

## tiltIndicatorAfter data common for all indicators

`ep_companies`, `ecoinvent_activities`, `matches_mapper`, and `ecoinvent_inputs` are the four datasets which are used as the input to the tiltIndicatorAfter package. They all are the output from tiltIndicatorBefore package. These four datasets are used for adding additional data to all the four indicators (PCTR, ICTR, PSTR, ISTR). 

```{r}
# ep_companies
ep_campanies_mapper <- read_csv("/path/to/input/ep_companies.csv") |>
  select("company_name", "country", "company_city", "postcode", "address", "main_activity", "companies_id") |>
  distinct()

# ecoinvent_activities
eco_act <- read_csv("/path/to/input/ei_activities_overview.csv")

# matches_mapper
match_map <- read_csv("/path/to/input/mapper_ep_ei.csv")

# ecoinvent_inputs
eco_inputs_raw <- read_csv("/path/to/input/ei_input_data.csv") |>
  select("input_activity_uuid_product_uuid", "exchange_name", "exchange_unit_name") |>
  distinct()
```

## PCTR

### Load Data

The input data of PCTR which comes from tiltIndicatorBefore package becomes the input for the tiltIndicator package.

```{r}
# PCTR companies
pctr_comp <- read_csv("/path/to/input/xctr_companies.csv", na = c("nan", NA)) |>
  rename(company_id = "companies_id") |>
  select(all_of(c("activity_uuid_product_uuid", "clustered", "company_id", "unit")))

# PCTR products
pctr_prod <- read_csv("/path/to/input/pctr_products.csv", col_types = cols(isic_4digit = col_character()), show_col_types = FALSE) |>
  select(all_of(c("co2_footprint", "tilt_sector", "unit", "isic_4digit", "activity_uuid_product_uuid", "ei_activity_name"))) |>
  filter(row_number() == 1L, .by = "activity_uuid_product_uuid")
```

### Create PCTR job for chunk operation

Multisession method will be used to create final outputs in chunks. Also, the `pctr_rds` function takes the output of tiltIndicator and use it as an input for the tiltIndicatorAfter package.

```{r}
# Create a "job" data frame where each row is a chunk of data
pctr_job <- pctr_comp |>
  nest_chunk(.by = "company_id", chunks = 1000) |>
  add_file(parent_product = cache_path("pctr/product"), parent_company = cache_path("pctr/company"))

pctr_rds <- function(data, file_product, file_company) {
  out <- xctr(data, pctr_prod)

  out |>
    unnest_product() |>
    prepare_pctr_product(ep_campanies_mapper, eco_act, match_map) |>
    write_rds(file_product)

  out |>
    unnest_company() |>
    prepare_pctr_company(unnest_product(out), ep_campanies_mapper, eco_act, match_map) |>
    write_rds(file_company)
}
```

### PCTR Job run

```{r}
pctr_job |>
  pick_undone() |>
  select(data, file_product, file_company) |>
  future_pwalk(pctr_rds, .progress = TRUE)
```

### Save the final PCTR final results

```{r}
pctr_product_result <- map_df(pctr_job$file_product, read_rds)
pctr_product_result |>
  write_csv("/path/to/output/pctr_product_result.csv")

pctr_company_result <- map_df(pctr_job$file_company, read_rds)
pctr_company_result |>
  write_csv("/path/to/output/pctr_company_result.csv")

# Each chunk result was saved to a file
dir_tree(cache_path("pctr/product"))
dir_tree(cache_path("pctr/company"))
```

## ICTR

### Load Data

The input data of ICTR which comes from tiltIndicatorBefore package becomes the input for the tiltIndicator package.

```{r}
ictr_comp <- read_csv("/path/to/input/xctr_companies.csv", na = c("nan", NA)) |>
  rename(company_id = "companies_id") |>
  select(all_of(c("activity_uuid_product_uuid", "clustered", "company_id", "unit"))) 

ictr_prod <- read_csv("/path/to/input/ictr_products.csv", col_types = cols(input_isic_4digit = col_character())) |>
  select(all_of(c("input_co2_footprint", "input_tilt_sector", "input_unit", "input_isic_4digit", "input_activity_uuid_product_uuid", "activity_uuid_product_uuid")))

is_na_free <- !anyNA(ictr_prod$input_co2_footprint)
stopifnot(is_na_free)
```

### Create ICTR job for chunk operation

Multisession method will be used to create final outputs in chunks. Also, the `ictr_rds` function takes the output of tiltIndicator and use it as an input for the tiltIndicatorAfter package.

```{r}
# Create a "job" data frame where each row is a chunk of data
ictr_job <- ictr_comp |>
  nest_chunk(.by = "company_id", chunks = 1000) |>
  add_file(parent_product = cache_path("ictr/product"), parent_company = cache_path("ictr/company"))

ictr_rds <- function(data, file_product, file_company) {
  out <- xctr(data, ictr_prod)

  out |>
    unnest_product() |>
    prepare_ictr_product(ep_campanies_mapper, eco_act, match_map, eco_inputs_raw) |>
    write_rds(file_product)

  out |>
    unnest_company() |>
    prepare_ictr_company(unnest_product(out), ep_campanies_mapper, eco_act, match_map, eco_inputs_raw) |>
    write_rds(file_company)
}
```

### ICTR Job run

```{r}
ictr_job |>
  pick_undone() |>
  select(data, file_product, file_company) |>
  future_pwalk(ictr_rds, .progress = TRUE)
```

### Save the final ICTR final results

```{r}
ictr_product_result <- map_df(ictr_job$file_product, read_rds)
ictr_product_result |>
  write_csv("/path/to/output/ictr_product_result.csv")

ictr_company_result <- map_df(ictr_job$file_company, read_rds)
ictr_company_result |>
  write_csv("/path/to/output/ictr_company_result.csv")

# Each chunk result was saved to a file
dir_tree(cache_path("ictr/product"))
dir_tree(cache_path("ictr/company"))
```

## PSTR

### Load Data

The input data of PSTR which comes from tiltIndicatorBefore package becomes the input for the tiltIndicator package.

```{r}
pstr_comp <- read_csv("/path/to/input/pstr_companies.csv", col_types = cols(isic_4digit = col_character()), col_select = -company_name, na = c("nan", NA)) |>
  rename(company_id = companies_id) |>
  xstr_prune_companies() |>
  xstr_pivot_type_sector_subsector()

ipr <- read_csv("/path/to/input/str_ipr_targets.csv")
weo <- read_csv("/path/to/input/str_weo_targets.csv")
scenarios_new <- list(ipr = ipr, weo = weo) |>
  xstr_prepare_scenario()
```

### Create PSTR job for chunk operation

Multisession method will be used to create final outputs in chunks. Also, the `pstr_rds` function takes the output of tiltIndicator and use it as an input for the tiltIndicatorAfter package.

```{r}
# Create a "job" data frame where each row is a chunk of data
pstr_job <- pstr_comp |>
  nest_chunk(.by = "company_id", chunks = 1000) |>
  add_file(parent_product = cache_path("pstr/product"), parent_company = cache_path("pstr/company"))

pstr_rds <- function(data, file_product, file_company) {
  out <- pstr(data, scenarios_new)

  out |>
    unnest_product() |>
    prepare_pstr_product(ep_campanies_mapper, eco_act, match_map) |>
    write_rds(file_product)

  out |>
    unnest_company() |>
    xstr_polish_output_at_company_level() |>
    prepare_pstr_company(unnest_product(out), ep_campanies_mapper, eco_act, match_map) |>
    write_rds(file_company)
}
```

### PSTR Job run

```{r}
pstr_job |>
  pick_undone() |>
  select(data, file_product, file_company) |>
  future_pwalk(pstr_rds, .progress = TRUE)
```

### Save the final PSTR final results

```{r}
pstr_product_result <- map_df(pstr_job$file_product, read_rds)
pstr_product_result |>
  write_csv("/path/to/output/pstr_product_result.csv")

pstr_company_result <- map_df(pstr_job$file_company, read_rds)
pstr_company_result |>
  write_csv("/path/to/output/pstr_company_result.csv")

# Each chunk result was saved to a file
dir_tree(cache_path("pstr/product"))
dir_tree(cache_path("pstr/company"))
```

## ISTR

### Load Data

The input data of ISTR which comes from tiltIndicatorBefore package becomes the input for the tiltIndicator package.

```{r}
istr_comp <- read_csv("/path/to/input/istr_companies.csv", na = c("nan", NA)) |>
  rename(company_id = "companies_id") |>
  xstr_prune_companies()

istr_inputs_raw <- read_csv("/path/to/input/istr_products.csv", col_types = cols(input_isic_4digit = col_character()), na = c("nan", NA)) |>
  rename(weo_sector = "input_weo_product", weo_subsector = "input_weo_flow", ipr_sector = "input_ipr_sector", ipr_subsector = "input_ipr_subsector") |>
  xstr_pivot_type_sector_subsector()

ipr <- read_csv("/path/to/input/str_ipr_targets.csv")
weo <- read_csv("/path/to/input/str_weo_targets.csv")
scenarios_new <- list(ipr = ipr, weo = weo) |>
  xstr_prepare_scenario()
```

### Create ISTR job for chunk operation

Multisession method will be used to create final outputs in chunks. Also, the `istr_rds` function takes the output of tiltIndicator and use it as an input for the tiltIndicatorAfter package.

```{r}
# Create a "job" data frame where each row is a chunk of data
istr_job <- istr_comp |>
  nest_chunk(.by = "company_id", chunks = 1000) |>
  add_file(parent_product = cache_path("istr/product"), parent_company = cache_path("istr/company"))

istr_rds <- function(data, file_product, file_company) {
  out <- istr(data, scenarios_new, istr_inputs_raw)

  out |>
    unnest_product() |>
    prepare_istr_product(ep_campanies_mapper, eco_act, match_map, eco_inputs_raw) |>
    write_rds(file_product)

  out |>
    unnest_company() |>
    xstr_polish_output_at_company_level() |>
    prepare_istr_company(unnest_product(out), ep_campanies_mapper, eco_act, match_map, eco_inputs_raw) |>
    write_rds(file_company)
}
```

### ISTR Job run

```{r}
istr_job |>
  pick_undone() |>
  select(data, file_product, file_company) |>
  future_pwalk(istr_rds, .progress = TRUE)
```

### Save the final ISTR final results

```{r}
istr_product_result <- map_df(istr_job$file_product, read_rds)
istr_product_result |>
  write_csv("/path/to/output/istr_product_result.csv")

istr_company_result <- map_df(istr_job$file_company, read_rds)
istr_company_result |>
  write_csv("/path/to/output/istr_company_result.csv")

# Each chunk result was saved to a file
dir_tree(cache_path("istr/product"))
dir_tree(cache_path("istr/company"))
```
