---
title: "tiltIndicatorAfter_runner_pctr"
author: "Kalash"
date: "2023-07-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup
```{r}
library(dplyr, warn.conflicts = FALSE)
library(readr, warn.conflicts = FALSE)
library(tidyr, warn.conflicts = FALSE)
library(purrr, warn.conflicts = FALSE)
library(rappdirs)
library(future)
library(furrr)
library(fs)
library(tiltIndicator)
## devtools::install_github("2DegreesInvesting/tiltIndicatorAfter")
library(tiltIndicatorAfter)
```

# Helper functions

```{r}
options(readr.show_col_types = FALSE)
# Enable computing over multiple workers in parallel
plan(multisession)

# Helpers ----

cache_path <- function(..., parent = cache_dir()) {
  path(parent, ...)
}

cache_dir <- function() {
  user_cache_dir(appname = "tiltIndicatorAfter")
}

nest_chunk <- function(data, .by, chunks) {
  data |>
    nest(.by = all_of(.by)) |>
    mutate(data, chunk = as.integer(cut(row_number(), chunks))) |>
    unnest(data) |>
    nest(.by = chunk)
}

add_file <- function(data, parent_product, parent_company, ext = ".rds") {
  dir_create(parent_product)
  dir_create(parent_company)
  mutate(data, file_product = path(parent_product, paste0(chunk, ext)), file_company = path(parent_company, paste0(chunk, ext)))
}

pick_undone <- function(data) {
  data |>
    add_done() |>
    filter(!done_product | !done_company)
}

add_done <- function(data, file_product, file_company) {
  mutate(data, done_product = file_exists(file_product), done_company = file_exists(file_company))
}

```

# tiltIndicatorAfter data common for all indicators

```{r}
# ep_companies
ep_campanies_mapper <- read_csv("/path/to/input/ep_companies.csv") |>
  select("company_name", "country", "company_city", "postcode", "address", "main_activity", "companies_id") |>
  distinct()

# ecoinvent_activities
eco_act <- read_csv("/path/to/input/ei_activities_overview.csv")

# matches_mapper
match_map <- read_csv("/path/to/input/mapper_ep_ei.csv")

# ecoinvent_inputs
eco_inputs_raw <- read_csv("/path/to/input/ei_input_data.csv") |>
  select("input_activity_uuid_product_uuid", "exchange_name", "exchange_unit_name") |>
  distinct()
```

# PCTR

## Load Data

Input data for tiltIndicator package is loaded

```{r}
# PCTR companies
pctr_comp <- read_csv("/path/to/input/xctr_companies.csv", na = c("nan", NA)) |>
  rename(company_id = "companies_id") |>
  select(all_of(c("activity_uuid_product_uuid", "clustered", "company_id", "unit")))

# PCTR products
pctr_prod <- read_csv("/path/to/input/pctr_products.csv", col_types = cols(isic_4digit = col_character()), show_col_types = FALSE) |>
  select(all_of(c("co2_footprint", "tilt_sector", "unit", "isic_4digit", "activity_uuid_product_uuid", "ei_activity_name"))) |>
  filter(row_number() == 1L, .by = "activity_uuid_product_uuid")
```

## Create PCTR job for chunk operation

```{r}
# Create a "job" data frame where each row is a chunk of data
pctr_job <- pctr_comp |>
  nest_chunk(.by = "company_id", chunks = 1000) |>
  add_file(parent_product = cache_path("pctr/product"), parent_company = cache_path("pctr/company"))

pctr_rds <- function(data, file_product, file_company) {
  out <- xctr(data, pctr_prod)

  out |>
    unnest_product() |>
    prepare_pctr_product(ep_campanies_mapper, eco_act, match_map) |>
    write_rds(file_product)

  out |>
    unnest_company() |>
    prepare_pctr_company(unnest_product(out), ep_campanies_mapper, eco_act, match_map) |>
    write_rds(file_company)
}
```

## PCTR Job run

```{r}
pctr_job |>
  pick_undone() |>
  select(data, file_product, file_company) |>
  future_pwalk(pctr_rds, .progress = TRUE)
```

## Save the final PCTR final results

```{r}
pctr_product_result <- map_df(pctr_job$file_product, read_rds)
pctr_product_result |>
  write_csv("/path/to/output/pctr_product_result.csv")

pctr_company_result <- map_df(pctr_job$file_company, read_rds)
pctr_company_result |>
  write_csv("/path/to/output/pctr_company_result.csv")

# Each chunk result was saved to a file
dir_tree(cache_path("pctr/product"))
dir_tree(cache_path("pctr/company"))
```

# ICTR

## Load Data

```{r}
ictr_comp <- read_csv("/path/to/input/xctr_companies.csv", na = c("nan", NA)) |>
  rename(company_id = "companies_id") |>
  select(all_of(c(
    "activity_uuid_product_uuid",
    "clustered",
    "company_id",
    "unit"
  ))) 

ictr_prod <- read_csv("/path/to/input/ictr_products.csv", col_types = cols(input_isic_4digit = col_character())) |>
  select(all_of(c(
    "input_co2_footprint",
    "input_tilt_sector",
    "input_unit",
    "input_isic_4digit",
    "input_activity_uuid_product_uuid",
    "activity_uuid_product_uuid"
  )))

is_na_free <- !anyNA(ictr_prod$input_co2_footprint)
stopifnot(is_na_free)
```

## Create ICTR job for chunk operation

```{r}
# Create a "job" data frame where each row is a chunk of data
ictr_job <- ictr_comp |>
  nest_chunk(.by = "company_id", chunks = 1000) |>
  add_file(parent_product = cache_path("ictr/product"), parent_company = cache_path("ictr/company"))

ictr_rds <- function(data, file_product, file_company) {
  out <- xctr(data, ictr_prod)

  out |>
    unnest_product() |>
    prepare_ictr_product(ep_campanies_mapper, eco_act, match_map, eco_inputs_raw) |>
    write_rds(file_product)

  out |>
    unnest_company() |>
    prepare_ictr_company(unnest_product(out), ep_campanies_mapper, eco_act, match_map, eco_inputs_raw) |>
    write_rds(file_company)
}
```

## ICTR Job run

```{r}
ictr_job |>
  pick_undone() |>
  select(data, file_product, file_company) |>
  future_pwalk(ictr_rds, .progress = TRUE)
```

## Save the final ICTR final results

```{r}
ictr_product_result <- map_df(ictr_job$file_product, read_rds)
ictr_product_result |>
  write_csv("/path/to/output/ictr_product_result.csv")

ictr_company_result <- map_df(ictr_job$file_company, read_rds)
ictr_company_result |>
  write_csv("/path/to/output/ictr_company_result.csv")

# Each chunk result was saved to a file
dir_tree(cache_path("ictr/product"))
dir_tree(cache_path("ictr/company"))
```

# PSTR

## Load Data

```{r}
pstr_comp <- read_csv("/path/to/input/pstr_companies.csv", col_types = cols(isic_4digit = col_character()), col_select = -company_name, na = c("nan", NA)) |>
  rename(company_id = companies_id) |>
  # rename(weo_product = weo_sector) |>
  # rename(weo_flow = weo_subsector) |>
  xstr_prune_companies() |>
  xstr_pivot_type_sector_subsector()

ipr <- read_csv("/path/to/input/str_ipr_targets.csv")
weo <- read_csv("/path/to/input/str_weo_targets.csv") |>
  mutate(co2_reductions = stringr::str_extract(co2_reductions, "-?\\d+\\.\\d+")) |>
  mutate(co2_reductions = as.numeric(co2_reductions)) |>
  mutate(co2_reductions = round(co2_reductions/100, digits = 2))
scenarios_new <- list(ipr = ipr, weo = weo) |>
  xstr_prepare_scenario()
```

## Create PSTR job for chunk operation

```{r}
# Create a "job" data frame where each row is a chunk of data
pstr_job <- pstr_comp |>
  nest_chunk(.by = "company_id", chunks = 1000) |>
  add_file(parent_product = cache_path("pstr/product"), parent_company = cache_path("pstr/company"))

pstr_rds <- function(data, file_product, file_company) {
  out <- pstr(data, scenarios_new)

  out |>
    unnest_product() |>
    prepare_pstr_product(ep_campanies_mapper, eco_act, match_map) |>
    write_rds(file_product)

  out |>
    unnest_company() |>
    xstr_polish_output_at_company_level() |>
    prepare_pstr_company(unnest_product(out), ep_campanies_mapper, eco_act, match_map) |>
    write_rds(file_company)
}
```

## PSTR Job run

```{r}
pstr_job |>
  pick_undone() |>
  select(data, file_product, file_company) |>
  future_pwalk(pstr_rds, .progress = TRUE)
```

## Save the final PSTR final results

```{r}
pstr_product_result <- map_df(pstr_job$file_product, read_rds)
pstr_product_result |>
  write_csv("/path/to/output/pstr_product_result.csv")

pstr_company_result <- map_df(pstr_job$file_company, read_rds)
pstr_company_result |>
  write_csv("/path/to/output/pstr_company_result.csv")

# Each chunk result was saved to a file
dir_tree(cache_path("pstr/product"))
dir_tree(cache_path("pstr/company"))
```

# ISTR

## Load Data

```{r}
istr_comp <- read_csv("/path/to/input/istr_companies.csv", na = c("nan", NA)) |>
  rename(company_id = "companies_id") |>
  xstr_prune_companies()

istr_inputs_raw <- read_csv("/path/to/input/istr_products.csv", col_types = cols(input_isic_4digit = col_character()), na = c("nan", NA)) |>
  rename(weo_product = "input_weo_product", weo_flow = "input_weo_flow", ipr_sector = "input_ipr_sector", ipr_subsector = "input_ipr_subsector") |>
  xstr_pivot_type_sector_subsector()

ipr <- read_csv("/path/to/input/str_ipr_targets.csv")
weo <- read_csv("/path/to/input/str_weo_targets.csv") |>
  mutate(co2_reductions = stringr::str_extract(co2_reductions, "-?\\d+\\.\\d+")) |>
  mutate(co2_reductions = as.numeric(co2_reductions)) |>
  mutate(co2_reductions = round(co2_reductions/100, digits = 2))
scenarios_new <- list(ipr = ipr, weo = weo) |>
  xstr_prepare_scenario()
```

## Create ISTR job for chunk operation

```{r}
# Create a "job" data frame where each row is a chunk of data
istr_job <- istr_comp |>
  nest_chunk(.by = "company_id", chunks = 1000) |>
  add_file(parent_product = cache_path("istr/product"), parent_company = cache_path("istr/company"))

istr_rds <- function(data, file_product, file_company) {
  out <- istr(data, scenarios_new, istr_inputs_raw)

  out |>
    unnest_product() |>
    prepare_istr_product(ep_campanies_mapper, eco_act, match_map, eco_inputs_raw) |>
    write_rds(file_product)

  out |>
    unnest_company() |>
    xstr_polish_output_at_company_level() |>
    prepare_istr_company(unnest_product(out), ep_campanies_mapper, eco_act, match_map, eco_inputs_raw) |>
    write_rds(file_company)
}
```

## ISTR Job run

```{r}
istr_job |>
  pick_undone() |>
  select(data, file_product, file_company) |>
  future_pwalk(istr_rds, .progress = TRUE)
```

## Save the final ISTR final results

```{r}
istr_product_result <- map_df(istr_job$file_product, read_rds)
istr_product_result |>
  write_csv("/path/to/output/istr_product_result.csv")

istr_company_result <- map_df(istr_job$file_company, read_rds)
istr_company_result |>
  write_csv("/path/to/output/istr_company_result.csv")

# Each chunk result was saved to a file
dir_tree(cache_path("istr/product"))
dir_tree(cache_path("istr/company"))
```
