---
title: "04_output_data_prep"
author: "Tilman"
date: "2023-05-10"
output: html_document
---

# Overview
Inputs from "output_tiltIndicator" + "input_data_clean" and outputs in "04_final_outputs".
Description: 
This script uses as input data the output of tiltIndicator (https://2degreesinvesting.github.io/tiltIndicator/). For sample data, you can install the package and run the indicators to obtain a smaller test dataset. 
The output this script produces are the final result dataframes of the 4 indicators (PSTR, ISTR, PCTR, ICTR). How the final dataframes are required to look, is documented here (tabs: 02-06):https://docs.google.com/spreadsheets/d/1K1thTMRg-k4DSdJy-G1RFY0islOQk70ToU3zmCKmvHM/edit#gid=1258737772 
The following things are done to transform in- to output: 
1. Join meta info on company (country, street, main activity, etc.) by matching with ep_companies via companies_id. 
2. Add additional info from Ecoinvent via activity_uuid_product_uuid.
3. Add certainty of matches via mapper_ep_ei. 
4. Remove NA rows but keep companies_id without results with one row. This script contains these steps completely for PCTR & ICTR. For the XSTR-family, there is an additional script from Mauro that does most of the steps separately for XSTR. https://github.com/2DegreesInvesting/tiltIndicator/blob/396_Fix-xstr-outputs/data-raw/396_fix-xstr-outputs.md


# Setup
```{r}
library(tidyr)
library(here)
library(readr)
library(dplyr)

```

# Load data
Note: run data prep for each indicator separately, otherwise it takes too much storage
```{r}
# required for all indicators
ei_activities_overview_2 <- read.csv(here("data-raw/ei_activities_overview_2.csv"))
ep_companies_2 <- read_csv(here("data-raw/sample_input_datasets/ep_companies_2_sample.csv"))
mapper_ep_ei <- read_csv(here("data-raw/mapper_ep_ei.csv"))
ei_input_data_2 <- read_csv(here("data-raw/ei_input_data_2.csv"))

# XCTR: indicator output from tiltIndicator package
 pctr_product_level <- read_csv(here("data-raw/sample_input_datasets/pctr_product_level_sample.csv"))
 pctr_company_level <- read_csv(here("data-raw/sample_input_datasets/pctr_company_level_sample.csv"))
 ictr_product_level <- read_csv(here("data-raw/sample_input_datasets/ictr_product_level_sample.csv"))
 ictr_company_level <- read_csv(here("data-raw/sample_input_datasets/ictr_company_level_sample.csv"))

# XSTR: indicator output from tiltIndicator package, after modifications with this script: https://github.com/2DegreesInvesting/tiltIndicator/blob/396_Fix-xstr-outputs/data-raw/396_fix-xstr-outputs.md 
  # load cleaned PSTR results from: https://github.com/2DegreesInvesting/tiltIndicator/pull/397
  pstr_product_level <- read_csv(here("data-raw/sample_input_datasets/pstr_product_level_sample.csv"))
  pstr_company_level <- read_csv(here("data-raw/sample_input_datasets/pstr_company_level_sample.csv"))
  istr_product_level <- read_csv(here("data-raw/sample_input_datasets/istr_product_level_sample.csv"))
  istr_company_level <- read_csv(here("data-raw/sample_input_datasets/istr_company_level_sample.csv"))
```

# Prepare mapper_ep_ei for multiple matches
The mapper indicates multiple matches with multi_match == TRUE. That means that for every combination of country, main_activity, and clustered, there are multiple matches, i.e. multiple rows. We will now aggregate these multiple rows together. 
```{r}
# first join activity_name, reference_product_name, and unit to mapper
mapper_ep_ei <- mapper_ep_ei |> 
  left_join(select(ei_activities_overview_2, activity_uuid_product_uuid, activity_name, 
                   reference_product_name, unit), by = "activity_uuid_product_uuid")

# now aggregate for multiple matches of country, main_activity, clustered
mapper_ep_ei <- mapper_ep_ei |> 
 group_by(country, main_activity, clustered) |> 
  summarise(across(everything(), ~ paste0(na.omit(unique(.)), collapse = "; "))) |>
  ungroup() |> 
  distinct()

# replace empty cells with FALSE
mapper_ep_ei <- mutate(mapper_ep_ei, multi_match = case_when(
  multi_match == "" ~ "FALSE", 
  TRUE   ~ multi_match 
))
#mapper_ep_ei$multi_match[mapper_ep_ei$multi_match==""] <- FALSE

unique(mapper_ep_ei$multi_match)

# assure that "completion" column is not aggregated wrongly and still shows "low", "medium", "high"
unique(mapper_ep_ei$completion)

mapper_ep_ei |> distinct(activity_uuid_product_uuid)

```


# 1. PCTR product-level preparation
## Joining relevant datasets
Join via companies_id
- postcode
- street_name
- country
- main_activity
Join via activity_uuid_product_uuid 
- matched_activity_name
- matched_reference_product
Join via mapper_ep_ei
- matching certainty
```{r}
# Get c("postcode", "street_name", "country", "main_activity") via "companies_id". 
pctr_product_level_2 <- pctr_product_level |> 
  left_join(select(ep_companies_2, c("company_name","country", "company_city", "postcode", 
                                     "address","main_activity", "companies_id")), by = "companies_id", relationship = "many-to-many") |> 
  relocate(companies_id, company_name, country, company_city, postcode, address, main_activity, clustered, 
           activity_uuid_product_uuid, grouped_by, risk_category, co2_footprint) |> 
  distinct() 

# ep_companies_2 <- ep_companies_2 |> select("company_name","country", "company_city", "postcode", 
#                                      "address","main_activity", "companies_id") |>
#   distinct()
# pctr_product_level_3 <- pctr_product_level |> 
#   left_join(ep_companies_2, by = "companies_id") 


rm(pctr_product_level)

# get isic_sectors (can potentially be skipped as we get most info via mapper_ep_ei in the next step)
pctr_product_level_3 <- pctr_product_level_2 |> 
  left_join(select(ei_activities_overview_2, activity_uuid_product_uuid, isic_4digit, 
                   isic_4digit_name_ecoinvent, isic_section), by = "activity_uuid_product_uuid")

rm(pctr_product_level_2)

# get matching certainty + activity_name + reference_product_name + unit
pctr_product_level_4 <- pctr_product_level_3 |> 
  left_join(select(mapper_ep_ei, c(
    "country", "main_activity", "clustered", "activity_uuid_product_uuid", "multi_match", "completion", "activity_name", "reference_product_name", "unit")), 
            by = c("country", "main_activity", "clustered", "activity_uuid_product_uuid")) |> 
  rename(matching_certainty = completion) |>
  mutate(matching_certainty_num = case_when(
    matching_certainty == "low" ~ 0, 
    matching_certainty == "medium" ~ 0.5, 
    matching_certainty == "high" ~ 1, 
  ))

rm(pctr_product_level_3)

# create new column with company-level averages for matching_certainty
pctr_product_level_5 <- pctr_product_level_4 |> 
  group_by(companies_id) |>
  mutate(avg_matching_certainty_num = mean(matching_certainty_num, na.rm = TRUE)) |> 
  ungroup()

rm(pctr_product_level_4)

# create column with "low", "medium", "high" values for company averages
pctr_product_level_6 <- pctr_product_level_5 |> 
    mutate(avg_matching_certainty = ifelse(
    avg_matching_certainty_num > 2/3, "high",
    ifelse(avg_matching_certainty_num > 1/3, "medium", "low")
  ))  

rm(pctr_product_level_5)

```

## Final product-level dataframe
```{r}
# final order & names
pctr_product_level_7 <- pctr_product_level_6 |> 
  relocate(companies_id, company_name, country, risk_category, grouped_by, clustered, activity_name, reference_product_name, 
           unit, multi_match, matching_certainty, avg_matching_certainty, 
           co2_footprint, company_city, postcode, address, main_activity, 
            activity_uuid_product_uuid) |>
  rename(
    matched_activity_name = activity_name,
    matched_reference_product = reference_product_name,
    matching_certainty_company_average = avg_matching_certainty, 
    benchmark = grouped_by, 
    PCTR_risk_category = risk_category) |> 
  select(-isic_4digit, -isic_4digit_name_ecoinvent, -isic_section, -matching_certainty_num, -avg_matching_certainty_num, -co2_footprint) |>
  distinct()

# for companies without values in all PCTR_risk_category, delete every row except the first one
pctr_product_level_8 <- pctr_product_level_7 |> 
  group_by(companies_id) |>
  mutate(has_na = all(is.na(PCTR_risk_category)), row_number = row_number()) |>
  ungroup() |>
  mutate(benchmark = ifelse(has_na & row_number != 1, NA, benchmark)) |>
  select(-has_na, -row_number) |> 
  filter(!is.na(benchmark))

# now remove values in "benchmark" when "PCTR_risk_category" is NA
pctr_product_level_final <- pctr_product_level_8 |> 
  group_by(companies_id) |>
  mutate(benchmark = ifelse(is.na(PCTR_risk_category), NA, benchmark)) |> 
  ungroup() |> 
  distinct() |> 
  arrange(country)

pctr_product_level_final <- pctr_product_level_final |> 
  rename(ep_product = clustered)

pctr_product_level_final |> filter(is.na(multi_match))

#write_csv(pctr_product_level_final, here("04_final_outputs/pctr_product_level_final_v4.csv"))
#pctr_product_level_final <- read_csv(here("04_final_outputs/pctr_product_level_final_v2.csv"))

```

# 2. PCTR company-level preparation
## Joining relevant datasets
Join column "matching_certainty" via 
```{r}
# create dataset containing c("companies_id", "avg_matching_certainty")
pctr_company_avg_match_cert <- pctr_product_level_6 |> 
  select("companies_id","company_name","company_city","country","postcode","address", "main_activity", "avg_matching_certainty") |> 
  distinct()

# join "avg_matching_certainty" to pctr_company_level via "companies_id"
pctr_company_level_2 <- pctr_company_level |> 
  left_join(pctr_company_avg_match_cert, by = "companies_id")

```

## Final company-level results
Aligning with names & structure from: https://docs.google.com/spreadsheets/d/1K1thTMRg-k4DSdJy-G1RFY0islOQk70ToU3zmCKmvHM/edit#gid=1258737772
```{r}
pctr_company_level_3 <- pctr_company_level_2 |> 
  rename(PCTR_risk_category = risk_category, 
         benchmark = grouped_by, 
         PCTR_share = value, 
         matching_certainty_company_average = avg_matching_certainty) |> 
  relocate(companies_id, company_name, company_city, country, postcode, address, main_activity, PCTR_risk_category, benchmark, PCTR_share, matching_certainty_company_average) |> 
  distinct()

# for companies without values in all ICTR_risk_category, delete every row except the first one
pctr_company_level_4 <- pctr_company_level_3 |> 
  group_by(companies_id) |>
  mutate(has_na = all(is.na(PCTR_share)), row_number = row_number()) |>
  ungroup() |>
  mutate(benchmark = ifelse(has_na & row_number != 1, NA, benchmark)) |>
  select(-has_na, -row_number) |> 
  filter(!is.na(benchmark))

# now remove values in "benchmark" & "PCTR_risk_category" when "PCTR_share" is NA
# pctr_company_level_5 <- pctr_company_level_4 |> 
#   group_by(companies_id) |>
#   mutate(benchmark = ifelse(all(is.na(matching_certainty_company_average)), NA, benchmark)) |>
#   mutate(PCTR_risk_category = ifelse(all(is.na(matching_certainty_company_average)), NA, PCTR_risk_category)) |>
#   ungroup() |> 
#   distinct()

pctr_company_level_5 <- pctr_company_level_4 |> 
  mutate(PCTR_risk_category = ifelse(is.na(matching_certainty_company_average), NA, PCTR_risk_category),
         benchmark = ifelse(is.na(matching_certainty_company_average), NA, benchmark))

# test: does every companies_id either appear 1 or 18 times? 
test <- pctr_company_level_5 |> 
  group_by(companies_id) |> 
  filter(n() > 1 & n() < 18) |> 
  select(companies_id)

# re-order columns
pctr_company_level_final <- pctr_company_level_5 |> 
  relocate(companies_id, company_name, country, PCTR_share, PCTR_risk_category, 
           benchmark, matching_certainty_company_average, company_city, postcode, 
           address, main_activity) |> 
  arrange(companies_id)

#write_csv(pctr_company_level_final, here("04_final_outputs/pctr_company_level_final_v4.csv"))

```

##########################################################################################################

# 3. ICTR product-level preparation
## Joining relevant datasets
Join via companies_id
- postcode
- street_name
- country
- main_activity
Join via activity_uuid_product_uuid 
- matched_activity_name
- matched_reference_product
Join via mapper_ep_ei
- matching certainty
```{r}
# prep of smaller inputs table for join
ei_inputs_small <- ei_input_data_2 |> 
  select(input_activity_uuid_product_uuid, exchange_name, exchange_unit_name) |> 
  distinct()

# # get c("activity_name", "unit") for inputs
ictr_product_level_2 <- ictr_product_level |> 
  left_join(select(ei_inputs_small, input_activity_uuid_product_uuid, exchange_name, exchange_unit_name), by = "input_activity_uuid_product_uuid")|>
  distinct()

rm(ei_input_data_2)

# remove "input_activity_uuid_product_uuid" and remove duplicates to reduce size
ictr_product_level_3 <- ictr_product_level_2 |> 
  select(-input_activity_uuid_product_uuid, -input_co2_footprint) |> 
  distinct()

rm(ictr_product_level)
rm(ictr_product_level_2)

```

## join with ep_companies_2 in chunks
```{r}
chunks <- 4
chunked <- ictr_product_level_3 %>% mutate(chunk = as.integer(cut(row_number(), chunks)))

chunk_1 <- filter(chunked, chunk == 1)
chunk_2 <- filter(chunked, chunk == 2)
chunk_3 <- filter(chunked, chunk == 3)
chunk_4 <- filter(chunked, chunk == 4)

# Get c("postcode", "street_name", "country", "main_activity") via "companies_id". 
ictr_product_level_4.1 <- chunk_1 |>
  left_join(select(ep_companies_2, c("company_name","country", "company_city", "postcode", 
                                     "address","main_activity", "companies_id")), by = "companies_id") |> 
  relocate(companies_id, company_name, country, company_city, postcode, address, main_activity, clustered, 
           activity_uuid_product_uuid, grouped_by, risk_category) |> 
  distinct() 

write_csv(ictr_product_level_4.1, here("04_final_outputs/temp/ictr_product_level_4.1.csv"))


ictr_product_level_4.2 <- chunk_2 |>
  left_join(select(ep_companies_2, c("company_name","country", "company_city", "postcode", 
                                     "address","main_activity", "companies_id")), by = "companies_id") |> 
  relocate(companies_id, company_name, country, company_city, postcode, address, main_activity, clustered, 
           activity_uuid_product_uuid, grouped_by, risk_category) |> 
  distinct() 

write_csv(ictr_product_level_4.2, here("04_final_outputs/temp/ictr_product_level_4.2.csv"))


ictr_product_level_4.3 <- chunk_3 |>
  left_join(select(ep_companies_2, c("company_name","country", "company_city", "postcode", 
                                     "address","main_activity", "companies_id")), by = "companies_id") |> 
  relocate(companies_id, company_name, country, company_city, postcode, address, main_activity, clustered, 
           activity_uuid_product_uuid, grouped_by, risk_category) |> 
  distinct() 

write_csv(ictr_product_level_4.3, here("04_final_outputs/temp/ictr_product_level_4.3.csv"))


ictr_product_level_4.4 <- chunk_4 |>
  left_join(select(ep_companies_2, c("company_name","country", "company_city", "postcode", 
                                     "address","main_activity", "companies_id")), by = "companies_id") |> 
  relocate(companies_id, company_name, country, company_city, postcode, address, main_activity, clustered, 
           activity_uuid_product_uuid, grouped_by, risk_category) |> 
  distinct() 

write_csv(ictr_product_level_4.4, here("04_final_outputs/temp/ictr_product_level_4.4.csv"))

```


# ANCHOR point: bind datasets together
```{r}
ictr_product_level_4.1 <- read_csv(here("04_final_outputs/temp/ictr_product_level_4.1.csv"))
ictr_product_level_4.2 <- read_csv(here("04_final_outputs/temp/ictr_product_level_4.2.csv"))
ictr_product_level_4.3 <- read_csv(here("04_final_outputs/temp/ictr_product_level_4.3.csv"))
ictr_product_level_4.4 <- read_csv(here("04_final_outputs/temp/ictr_product_level_4.4.csv"))

ictr_product_level_4 <- bind_rows(ictr_product_level_4.1, ictr_product_level_4.2, ictr_product_level_4.3, ictr_product_level_4.4)


rm(ictr_product_level_3)
rm(ictr_product_level_4.1)
rm(ictr_product_level_4.2)
rm(ictr_product_level_4.3)
rm(ictr_product_level_4.4)
rm(chunk_1)
rm(chunk_2)
rm(chunk_3)
rm(chunk_4)
rm(chunked)
```


## additional joins
```{r}
# get c("matched_activity_name", "unit", sectors) for matched products
ictr_product_level_5 <- ictr_product_level_4 |> 
  left_join(ei_activities_overview_2, by = "activity_uuid_product_uuid") 

rm(ictr_product_level_4)

ictr_product_level_6 <- ictr_product_level_5 |> 
  left_join(select(mapper_ep_ei, c(
    "country", "main_activity", "clustered", "activity_uuid_product_uuid", "multi_match", "completion")), 
            by = c("country", "main_activity", "clustered", "activity_uuid_product_uuid")) |> 
  rename(matching_certainty = completion) |>
  mutate(matching_certainty_num = case_when(
    matching_certainty == "low" ~ 0, 
    matching_certainty == "medium" ~ 0.5, 
    matching_certainty == "high" ~ 1, 
  )) |> 
  distinct()

rm(ictr_product_level_5)

# create new column with company-level averages for matching_certainty
ictr_product_level_7 <- ictr_product_level_6 |> 
  group_by(companies_id) |>
  mutate(avg_matching_certainty_num = mean(matching_certainty_num, na.rm = TRUE)) |> 
  ungroup()

rm(ictr_product_level_6)

# create column with "low", "medium", "high" values for company averages
ictr_product_level_8 <- ictr_product_level_7 |> 
    mutate(avg_matching_certainty = ifelse(
    avg_matching_certainty_num > 2/3, "high",
    ifelse(avg_matching_certainty_num > 1/3, "medium", "low")
  ))

rm(ictr_product_level_7)


```

## Final product-level dataframe
```{r}

ictr_product_level_9 <- ictr_product_level_8 |> 
  relocate(companies_id, company_name, country, risk_category, grouped_by, clustered, activity_name, 
           reference_product_name , unit, multi_match, matching_certainty, 
           avg_matching_certainty, exchange_name, exchange_unit_name, company_city, postcode, address, 
           main_activity, activity_uuid_product_uuid) |>
  rename(
    matched_activity_name = activity_name, 
    matched_reference_product = reference_product_name, 
    matching_certainty_company_average = avg_matching_certainty, 
    benchmark = grouped_by, 
    ICTR_risk_category = risk_category, 
    input_name = exchange_name, 
    input_unit = exchange_unit_name) |> 
  select(-isic_4digit, -isic_4digit_name_ecoinvent, -isic_section, -matching_certainty_num, -avg_matching_certainty_num) |>
  distinct() |> 
  arrange(country)

# for companies without values in all ICTR_risk_category, delete every row except the first one
ictr_product_level_10 <- ictr_product_level_9 |> 
  group_by(companies_id) |>
  mutate(has_na = all(is.na(ICTR_risk_category)), row_number = row_number()) |>
  ungroup() |>
  mutate(benchmark = ifelse(has_na & row_number != 1, NA, benchmark)) |>
  select(-has_na, -row_number) |> 
  filter(!is.na(benchmark))

# now remove values in "benchmark" when "ICTR_risk_category" is NA
ictr_product_level_final <- ictr_product_level_10 |> 
  group_by(companies_id) |>
  mutate(benchmark = ifelse(is.na(ICTR_risk_category), NA, benchmark)) |> 
  distinct() 

ictr_product_level_final <- ictr_product_level_final |> 
  rename(ep_product = clustered) |> 
  select(-chunk)


#write_csv(ictr_product_level_final, here("04_final_outputs/ictr_product_level_final_v4.csv"))
#ictr_product_level_final <- read_csv(here("04_final_outputs/ictr_product_level_final_v4.csv"))

rm(ictr_product_level_8)
rm(ictr_product_level_9)
rm(ictr_product_level_10)

```

# 4. ICTR company-level preparation
## Joining relevant datasets
Join column "matching_certainty" via 
```{r}
# create dataset containing c("companies_id", "avg_matching_certainty")
ictr_companies_avg_match_cert <- ictr_product_level_final |> 
  select("companies_id","company_name","company_city","country","postcode",
         "address", "main_activity", "matching_certainty_company_average") |> 
  distinct()

# join "avg_matching_certainty" to ictr_company_level via "companies_id"
ictr_company_level_2 <- ictr_company_level |> 
  left_join(ictr_companies_avg_match_cert, by = "companies_id")

```

## Final company-level results
Aligning with names & structure from: https://docs.google.com/spreadsheets/d/1K1thTMRg-k4DSdJy-G1RFY0islOQk70ToU3zmCKmvHM/edit#gid=1258737772
```{r}
ictr_company_level_3 <- ictr_company_level_2 |> 
  rename(ICTR_risk_category = risk_category, 
         benchmark = grouped_by, ICTR_share = value) |> 
  relocate(companies_id, company_name, company_city, country, ICTR_share, 
           ICTR_risk_category, benchmark, matching_certainty_company_average, 
           postcode, address, main_activity)|>
  distinct()

# for companies without values in all ICTR_risk_category, delete every row except the first one
ictr_company_level_4 <- ictr_company_level_3 |> 
  group_by(companies_id) |>
  mutate(has_na = all(is.na(ICTR_share)), row_number = row_number()) |>
  ungroup() |>
  mutate(benchmark = ifelse(has_na & row_number != 1, NA, benchmark)) |>
  select(-has_na, -row_number) |> 
  filter(!is.na(benchmark))

# now remove values in "benchmark" when "ICTR_risk_category" is NA
ictr_company_level_final <- ictr_company_level_4 |> 
  mutate(benchmark = ifelse(is.na(ICTR_share), NA, benchmark)) |>
  mutate(ICTR_risk_category = ifelse(is.na(ICTR_share), NA, ICTR_risk_category)) |>
  distinct()

#write_csv(ictr_company_level_final, here("04_final_outputs/ictr_company_level_final_v4.csv"))

```

# 5. PSTR product-level results
## cleaning from NAs
```{r}
no_NAs <- pstr_product_level |>
  filter(!is.na(risk_category)) 

# select company ids where all `risk_category` is only `NA`
ids <- pstr_product_level |>
  group_by(companies_id) |>
  filter(all(is.na(risk_category))) |>
  distinct(companies_id)

pstr_product_level <- bind_rows(no_NAs, ids)
```

## Joining relevant datasets
Join via companies_id
- postcode
- street_name
- country
- main_activity
Join via activity_uuid_product_uuid 
- matched_activity_name
- matched_reference_product
Join via mapper_ep_ei
- matching certainty
```{r}
# Get c("postcode", "street_name", "country", "main_activity") via "companies_id". 
pstr_product_level_2 <- pstr_product_level |> 
  left_join(select(ep_companies_2, c("company_name","country", "company_city", "postcode", 
                                     "address","main_activity", "companies_id")), by = "companies_id") |> 
  relocate(companies_id, company_name, country, company_city, postcode, address, main_activity, clustered, 
           activity_uuid_product_uuid, grouped_by, risk_category) |> 
  distinct() 

rm(pstr_product_level)

# get isic_sectors (can potentially be skipped as we get most info via mapper_ep_ei in the next step)
pstr_product_level_3 <- pstr_product_level_2 |> 
  left_join(select(ei_activities_overview_2, activity_uuid_product_uuid, activity_name, reference_product_name, isic_4digit, 
                   isic_4digit_name_ecoinvent, isic_section, unit), by = "activity_uuid_product_uuid")

rm(pstr_product_level_2)

# get matching certainty + activity_name + reference_product_name + unit
pstr_product_level_4 <- pstr_product_level_3 |> 
  left_join(select(mapper_ep_ei, c(
    "country", "main_activity", "clustered", "activity_uuid_product_uuid", "multi_match", "completion")), 
            by = c("country", "main_activity", "clustered", "activity_uuid_product_uuid")) |> 
  rename(matching_certainty = completion) |>
  mutate(matching_certainty_num = case_when(
    matching_certainty == "low" ~ 0, 
    matching_certainty == "medium" ~ 0.5, 
    matching_certainty == "high" ~ 1, 
  ))

rm(pstr_product_level_3)

# create new column with company-level averages for matching_certainty
pstr_product_level_5 <- pstr_product_level_4 |> 
  group_by(companies_id) |>
  mutate(avg_matching_certainty_num = mean(matching_certainty_num, na.rm = TRUE)) |> 
  ungroup()

rm(pstr_product_level_4)

# create column with "low", "medium", "high" values for company averages
pstr_product_level_6 <- pstr_product_level_5 |> 
    mutate(avg_matching_certainty = ifelse(
    avg_matching_certainty_num > 2/3, "high",
    ifelse(avg_matching_certainty_num > 1/3, "medium", "low")
  ))  

rm(pstr_product_level_5)

```

## Final product-level dataframe
```{r}
# final order & names
pstr_product_level_final <- pstr_product_level_6 |> 
  relocate(companies_id, company_name, country, risk_category, scenario, year, clustered, activity_name, reference_product_name, 
           unit, tilt_sector, tilt_subsector, multi_match, matching_certainty, avg_matching_certainty, company_city, postcode, address, main_activity, 
            activity_uuid_product_uuid) |>
  rename(
    matched_activity_name = activity_name,
    matched_reference_product = reference_product_name,
    matching_certainty_company_average = avg_matching_certainty, 
    PSTR_risk_category = risk_category, 
    ep_product = clustered) |> 
  select(-isic_4digit, -isic_4digit_name_ecoinvent, -isic_section, 
         -matching_certainty_num, -avg_matching_certainty_num, -grouped_by, -type) |> 
  mutate(scenario = ifelse(scenario == "1.5c rps", "IPR 1.5c RPS", scenario)) |> 
  mutate(scenario = ifelse(scenario == "nz 2050", "WEO NZ 2050", scenario)) |>
  distinct()

#write_csv(pstr_product_level_final, here("04_final_outputs/pstr_product_level_final.csv"))
#pstr_product_level_final <- read_csv(here("04_final_outputs/pstr_product_level_final.csv"))

```

# 6. PSTR company-level results
## Joining relevant datasets
Join column "matching_certainty" via 
```{r}
# create dataset containing c("companies_id", "avg_matching_certainty")
pstr_company_avg_match_cert <- pstr_product_level_6 |> 
  select("companies_id","company_name","company_city","country","postcode","address", "main_activity", "avg_matching_certainty") |>
  distinct()

# join "avg_matching_certainty" to pctr_company_level via "companies_id"
pstr_company_level_2 <- pstr_company_level |> 
  left_join(pstr_company_avg_match_cert, by = "companies_id") |> 
  distinct()

```

## Final company-level results
Aligning with names & structure from: https://docs.google.com/spreadsheets/d/1K1thTMRg-k4DSdJy-G1RFY0islOQk70ToU3zmCKmvHM/edit#gid=1258737772
```{r}
# rename and relocate
pstr_company_level_3 <- pstr_company_level_2 |> 
  rename(PSTR_risk_category = risk_category, 
         PSTR_share = value, 
         matching_certainty_company_average = avg_matching_certainty) |> 
  mutate(scenario = ifelse(scenario == "1.5c rps", "IPR 1.5c RPS", scenario)) |> 
  mutate(scenario = ifelse(scenario == "nz 2050", "WEO NZ 2050", scenario)) |> 
  select(-type) |>
  distinct()

# re-order columns
pstr_company_level_final <- pstr_company_level_3 |> 
  relocate(companies_id, company_name, country, PSTR_share, PSTR_risk_category, 
           scenario, year, matching_certainty_company_average, company_city, postcode, 
           address, main_activity) |> 
  arrange(companies_id)

#write_csv(pstr_company_level_final, here("04_final_outputs/pstr_company_level_final.csv"))

```

# 7. ISTR product-level results
## Joining relevant datasets
Join via companies_id
- postcode
- street_name
- country
- main_activity
Join via activity_uuid_product_uuid 
- matched_activity_name
- matched_reference_product
Join via mapper_ep_ei
- matching certainty
```{r}
# prep of smaller inputs table for join
ei_inputs_small <- ei_input_data_2 |> 
  select(input_activity_uuid_product_uuid, exchange_name, exchange_unit_name) |> 
  distinct()

# # get c("activity_name", "unit") for inputs
istr_product_level_2 <- istr_product_level |> 
  left_join(select(ei_inputs_small, input_activity_uuid_product_uuid, exchange_name, exchange_unit_name), by = "input_activity_uuid_product_uuid")|>
  distinct()

rm(ei_input_data_2)

# remove "input_activity_uuid_product_uuid" and remove duplicates to reduce size
istr_product_level_3 <- istr_product_level_2 |> 
  select(-input_activity_uuid_product_uuid) |> 
  distinct()

rm(istr_product_level)
rm(istr_product_level_2)

```

## join with ep_companies_2 in chunks
```{r}
chunks <- 4
chunked <- istr_product_level_3 %>% mutate(chunk = as.integer(cut(row_number(), chunks)))

chunk_1 <- filter(chunked, chunk == 1)
chunk_2 <- filter(chunked, chunk == 2)
chunk_3 <- filter(chunked, chunk == 3)
chunk_4 <- filter(chunked, chunk == 4)

# Get c("postcode", "street_name", "country", "main_activity") via "companies_id". 
istr_product_level_4.1 <- chunk_1 |>
  left_join(select(ep_companies_2, c("company_name","country", "company_city", "postcode", 
                                     "address","main_activity", "companies_id")), by = "companies_id") |> 
  relocate(companies_id, company_name, country, company_city, postcode, address, main_activity, clustered, 
           activity_uuid_product_uuid, grouped_by, risk_category) |> 
  distinct() 

write_csv(istr_product_level_4.1, here("04_final_outputs/temp/istr_product_level_4.1.csv"))


istr_product_level_4.2 <- chunk_2 |>
  left_join(select(ep_companies_2, c("company_name","country", "company_city", "postcode", 
                                     "address","main_activity", "companies_id")), by = "companies_id") |> 
  relocate(companies_id, company_name, country, company_city, postcode, address, main_activity, clustered, 
           activity_uuid_product_uuid, grouped_by, risk_category) |> 
  distinct() 

write_csv(istr_product_level_4.2, here("04_final_outputs/temp/istr_product_level_4.2.csv"))


istr_product_level_4.3 <- chunk_3 |>
  left_join(select(ep_companies_2, c("company_name","country", "company_city", "postcode", 
                                     "address","main_activity", "companies_id")), by = "companies_id") |> 
  relocate(companies_id, company_name, country, company_city, postcode, address, main_activity, clustered, 
           activity_uuid_product_uuid, grouped_by, risk_category) |> 
  distinct() 

write_csv(istr_product_level_4.3, here("04_final_outputs/temp/istr_product_level_4.3.csv"))


istr_product_level_4.4 <- chunk_4 |>
  left_join(select(ep_companies_2, c("company_name","country", "company_city", "postcode", 
                                     "address","main_activity", "companies_id")), by = "companies_id") |> 
  relocate(companies_id, company_name, country, company_city, postcode, address, main_activity, clustered, 
           activity_uuid_product_uuid, grouped_by, risk_category) |> 
  distinct() 

write_csv(istr_product_level_4.4, here("04_final_outputs/temp/istr_product_level_4.4.csv"))

```


# ANCHOR point: bind datasets together
```{r}
istr_product_level_4.1 <- read_csv(here("04_final_outputs/temp/istr_product_level_4.1.csv"))
istr_product_level_4.2 <- read_csv(here("04_final_outputs/temp/istr_product_level_4.2.csv"))
istr_product_level_4.3 <- read_csv(here("04_final_outputs/temp/istr_product_level_4.3.csv"))
istr_product_level_4.4 <- read_csv(here("04_final_outputs/temp/istr_product_level_4.4.csv"))

istr_product_level_4 <- bind_rows(istr_product_level_4.1, istr_product_level_4.2, istr_product_level_4.3, istr_product_level_4.4)


rm(istr_product_level_3)
rm(istr_product_level_4.1)
rm(istr_product_level_4.2)
rm(istr_product_level_4.3)
rm(istr_product_level_4.4)
rm(chunk_1)
rm(chunk_2)
rm(chunk_3)
rm(chunk_4)
rm(chunked)
```


## additional joins
```{r}
# get c("matched_activity_name", "unit", sectors) for matched products
istr_product_level_5 <- istr_product_level_4 |> 
  left_join(ei_activities_overview_2, by = "activity_uuid_product_uuid") 

rm(istr_product_level_4)

istr_product_level_6 <- istr_product_level_5 |> 
  left_join(select(mapper_ep_ei, c(
    "country", "main_activity", "clustered", "activity_uuid_product_uuid", "multi_match", "completion")), 
            by = c("country", "main_activity", "clustered", "activity_uuid_product_uuid")) |> 
  rename(matching_certainty = completion) |>
  mutate(matching_certainty_num = case_when(
    matching_certainty == "low" ~ 0, 
    matching_certainty == "medium" ~ 0.5, 
    matching_certainty == "high" ~ 1, 
  )) |> 
  distinct()

rm(istr_product_level_5)

# create new column with company-level averages for matching_certainty
istr_product_level_7 <- istr_product_level_6 |> 
  group_by(companies_id) |>
  mutate(avg_matching_certainty_num = mean(matching_certainty_num, na.rm = TRUE)) |> 
  ungroup()

rm(istr_product_level_6)

# create column with "low", "medium", "high" values for company averages
istr_product_level_8 <- istr_product_level_7 |> 
    mutate(avg_matching_certainty = ifelse(
    avg_matching_certainty_num > 2/3, "high",
    ifelse(avg_matching_certainty_num > 1/3, "medium", "low")
  ))

rm(istr_product_level_7)


```

## Final product-level dataframe
```{r}

istr_product_level_9 <- istr_product_level_8 |> 
  relocate(companies_id, company_name, country, risk_category, scenario, year, clustered, activity_name, 
           reference_product_name , unit, tilt_sector, multi_match, matching_certainty, 
           avg_matching_certainty, exchange_name, exchange_unit_name, input_tilt_sector, input_tilt_subsector, company_city, postcode, address, 
           main_activity, activity_uuid_product_uuid, grouped_by) |>
  rename(
    matched_activity_name = activity_name, 
    matched_reference_product = reference_product_name, 
    matching_certainty_company_average = avg_matching_certainty, 
    benchmark = grouped_by, 
    ISTR_risk_category = risk_category, 
    input_name = exchange_name, 
    input_unit = exchange_unit_name) |> 
  select(-isic_4digit, -isic_4digit_name_ecoinvent, -isic_section, -matching_certainty_num, -avg_matching_certainty_num) |>
  distinct() |> 
  arrange(country)

# final dataset
istr_product_level_final <- istr_product_level_9 |> 
  relocate()
  rename(ep_product = clustered) |> 
  select(-chunk, -grouped_by)


# write_csv(istr_product_level_final, here("04_final_outputs/istr_product_level_final.csv"))
# istr_product_level_final <- read_csv(here("04_final_outputs/istr_product_level_final_v4.csv"))

rm(istr_product_level_8)
rm(istr_product_level_9)

```

# 8. ISTR company-level results
## Joining relevant datasets
Join column "matching_certainty" via 
```{r}
# create dataset containing c("companies_id", "avg_matching_certainty")
istr_companies_avg_match_cert <- istr_product_level_final |> 
  select("companies_id","company_name","company_city","country","postcode",
         "address", "main_activity", "matching_certainty_company_average") |> 
  distinct()

# join "avg_matching_certainty" to istr_company_level via "companies_id"
istr_company_level_2 <- istr_company_level |> 
  left_join(istr_companies_avg_match_cert, by = "companies_id")

```

## Final company-level results
Aligning with names & structure from: https://docs.google.com/spreadsheets/d/1K1thTMRg-k4DSdJy-G1RFY0islOQk70ToU3zmCKmvHM/edit#gid=1258737772
```{r}
istr_company_level_3 <- istr_company_level_2 |> 
  rename(ISTR_risk_category = risk_category, 
         benchmark = grouped_by, ISTR_share = value) |> 
  relocate(companies_id, company_name, company_city, country, ISTR_share, 
           ISTR_risk_category, scenario, year, matching_certainty_company_average, 
           postcode, address, main_activity)|>
  distinct()


#write_csv(ictr_company_level_final, here("04_final_outputs/ictr_company_level_final_v4.csv"))

```
